\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-22 trunk/europa.tex
skipped adding europa's AC-3 algorithm since it doesn't seem to be possible to add it at a level of detail consistent with the rest of the section. adding standard AC-3 algorithm doesn't add value.

\kcomment{add europa's AC-3 algorithm here}

@@

A \eu user can introduce new constraint types by implementing
specialized Constraint and Propagator classes in C++, however, \eu
provides a built-in with over 25 arithmetic, temporal, set and
resource constraint types so that a large number of problem domains
can be modeled without having to introduce new constraint
types. Tables \ref{tab:calconst}, \ref{tab:setconst},
\ref{tab:objhierarchy} and \ref{tab:misc} show various constraint
types.

>>>>

%\kcomment{add europa's AC-3 algorithm here}

@@

A \eu user can introduce new constraint types by implementing
specialized Constraint and Propagator classes in C++, however, \eu
provides a built-in Constraint Library with over 25 arithmetic, temporal, set and
resource constraint types so that a large number of problem domains
can be modeled without having to introduce new constraint
types. Tables \ref{tab:calconst}, \ref{tab:setconst},
\ref{tab:objhierarchy} and \ref{tab:misc} show various constraint
types.
